\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
wordsmith qualitative section to be pretty; shortened/reworded the procedure

\subsection{Recruitment}
We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). Our age statistics omit one participant who declined to disclose. All of our participants had at least some college education. Twelve were new users and 4 had previously used Tor Browser in some capacity.

@@

We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.

\subsection{Procedure} 
We ran the experiment in a meeting room at UC Berkeley. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC media player~\cite{vlc} to record the screen during the experiment. Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

Each one-hour session was run by at least two researchers. We started by informing the participant of the study, task, and risks (Appendix~\ref{qualitative-script}). After consenting to the experiment, we instructed the participant to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites were blocked. We explicitly tell the participant to use Tor to circumvent censorship. The worksheet (Appendix~\ref{participant-worksheet}) required answers from a censored website (Wikipedia) and an uncensored website (CNN). We chose Wikipedia and CNN because they were popular websites~\cite{alexa} and their likely familiarity would make the task seem less intimidating. After giving the instructions, the researchers left the room to minimize interactions and watched a live feed of the participant's screen.

>>>>

\subsection{Recruitment}
We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). Our age statistics omit one participant who declined to disclose their age. All of our participants had at least some college education. Twelve were new users and four had previously used Tor Browser in some capacity.

@@

As we performed the experiments, we distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.

\subsection{Procedure} 
We ran the experiments in a small room with a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment. We ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen before each participant.

We get informed consent by talking about the study, task, and risks (Appendix~\ref{qualitative-script}). Then the participant visited sample websites in a non-Tor browser to illustrate that some sites were blocked and instruct them to use Tor to circumvent censorship. Their task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visitng a censored website (Wikipedia) and an uncensored website (CNN). We chose Wikipedia and CNN because their likely familiarity~\cite{alexa}. After giving the instructions, the researchers left the room to minimize interactions and watched a live feed of the participant's screen.
